### 2014-06-02 ACL2014/system.tex
small edits

\begin{figure}
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

\subsection{Multi Probe \lsh}
\label{sec:mblsh}
As we discussed in Section \ref{subsec:resuseHash}, generating hash functions can be computationally expensive.
Since the memory required by the algorithm also scales linearly with $L$, the number of hash tables, it is desirable to have a small 
number of tables to reduce the memory footprint. The memory footprint of vanilla LSH is what makes it impractical for real applications. 
Here, we first describe four new variants of the vanilla \lsh algorithm motivated by the intuition in
\mblshf~\cite{LvVLDB07}. The aim of \mblshf is to obtain significantly higher recall than the vanilla \lsh while using
the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that
in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neigboring buckets
in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
Hamming distance from the bucket in which $q$ falls. The empirically show that these neighboring buckets contain the near neighbors with
very high probability. 
Note that, for the same number of hash tables \mblshf will require more number of probes since it searches for multiple buckets within a table. 
The main advantage of searching in multiple buckets over generating more number of tables 
is that it takes more memory and time to generate more tables in pre-processing.

>>>>

\begin{figure}
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with the same $g_j$ value ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

\subsection{Multi Probe \lsh}
\label{sec:mblsh}
As we discussed in Section \ref{subsec:resuseHash}, generating hash functions can be computationally expensive.
Since the memory required by the algorithm also scales linearly with $L$, the number of hash tables, it is desirable to have a small 
number of tables to reduce the memory footprint. The memory footprint of vanilla LSH is what makes it impractical for real applications. 
Here, we first describe four new variants of the vanilla \lsh algorithm motivated by the intuition in
\mblshf~\cite{LvVLDB07}. \mblshf obtains significantly higher recall than the vanilla \lsh while using
the same number of hash tables. In order to achieve this, the main intuition utilized in \mblshf is that
in addition to looking at the hash bucket that a test query $q$ falls in, it is also possible to look at the neigboring buckets
in order to find its near neigbour candidates. \mblshf in ~\cite{LvVLDB07} suggests exploring the neighboring buckets in order of the
Hamming distance from the bucket in which $q$ falls. The empirically show that these neighboring buckets contain the near neighbors with
very high probability. 
Note that, for the same number of hash tables \mblshf will require more number of probes since it searches for multiple buckets within a table. 
The main advantage of searching in multiple buckets over generating more number of tables 
is that it takes more memory and time to generate more tables in pre-processing.
